\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Added HRI and eye-tracking refs

Previous work also show a clear relation between gaze patterns and
task-based performance in collaborative settings. 
CITE RICK DALE

In a pair-programming task, \cite{jermann2012effects}
showed that the good performing pairs have more synchronised gaze on different
parts of a program than the bad performing pairs. In a similar task,
\cite{sharma2012gaze} showed that the good performing pairs pay more attention
to the data-flow of the program than the poor performing pairs. Moreover,
\cite{sharma2013understanding} showed that while describing the functionality of
a program the well performing teams had more gaze on the variable modification
parts in the program while poor performing teams have equal distribution of gaze
on different parts of the program during similar phase of the task.  Thus we see
that previous research provides insights about the relationship between the gaze
patterns and the behavioural and task-based performance indicators in diverse
scenarios.

@@

Controlling robot with gaze

@@

Physiological and subjective evaluation of a human?robot object hand-over task

>>>>

Previous work also show a clear relation between gaze patterns and
task-based performance in collaborative settings. As a measure of joint attention in collaborative settings  \cite{richardson2007art} proposed gaze recurrence between the collaborators and showed it to be correlated with the collaboration quality of the pair. In a pair-programming task, \cite{jermann2012effects} showed that the good performing pairs have more synchronised gaze on different parts of a program than the bad performing pairs. In a similar task, \cite{sharma2012gaze} showed that the good performing pairs pay more attention to the data-flow of the program than the poor performing pairs. Moreover, \cite{sharma2013understanding} showed that while describing the functionality of a program the well performing teams had more gaze on the variable modification parts in the program while poor performing teams have equal distribution of gaze on different parts of the program during similar phase of the task.  Thus we see that previous research provides insights about the relationship between the gaze patterns and the behavioural and task-based performance indicators in diverse scenarios.

@@

Controlling robot with gaze \cite{bhuiyan2004tracking}

@@

Physiological and subjective evaluation of a human-robot object hand-over task  \cite{dehais2011physiological}
